A Global Picture of Food Insecurity and Hunger

### 2020-09-11 docs/modeling_fies.tex
Updates from Overleaf

>>>>

Dynamics of population growth and development

Deal with scale - why modeling at admin1 is a different exercise than local level modeling

What is driving the increases?
What will drive the decreases? (caveats of RF method)

Next decade improvements in food insecurity will only fall like 10\%, not major in overall terms and nowhere near ambitious SDG target.

Cliamte change is not yet a major threat on a global scale, although there will be regional impacts
